Modeling workflow: NLA N2O survey data

### 2025-03-18 scripts/NLA_N2O_models.Rmd
Updated modeling script and documentation

```{r conditional_effects_mod_n2osat_temp_F, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
effect_no3_surftemp <- expand.grid(no3_cat = levels(df_model$no3_cat),
                               surftemp = round(quantile(df_model$surftemp, 
                                                   probs = seq(0.10, 0.90, 0.2)), 0),
                               log_area = mean(df_model$log_area),
                               log_elev = mean(df_model$log_elev)) %>%
  add_epred_draws(n2o_mod6, resp = c("n2o", "n2oeq"), re_formula = ~ 1) %>%
  pivot_wider(names_from = .category, values_from = .epred) %>%
  mutate(n2o_pred = n2o,
         n2oeq_pred = n2oeq,
         sat_pred = n2o / n2oeq,
         surftemp = factor(surftemp))

@@

legend1 <- get_legend(legend1)

@@

legend2 <- get_legend(legend2)

@@

```{r conditional_effects_mod_n2osat_area_F, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
effect_no3_area <- expand.grid(no3_cat = levels(df_model$no3_cat),
                               log_area = round(quantile(df_model$log_area, 
                                                   probs = seq(0.10, 0.90, 0.2)), 0),
                               surftemp = mean(df_model$surftemp),
                               log_elev = mean(df_model$log_elev)) %>%
  add_epred_draws(n2o_mod6, resp = c("n2o", "n2oeq"), re_formula = ~ 1) %>%
  pivot_wider(names_from = .category, values_from = .epred) %>%
  mutate(n2o_pred = n2o,
         n2oeq_pred = n2oeq,
         sat_pred = n2o / n2oeq,
         log_area = factor(log_area))

@@

```{r plot_area_effects, fig.align='center', fig.asp=1.166667, fig.width=8, }
plt_area_effects
```

```{r conditional_effects_mod_n2osat_temp_area_F, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
effect_no3_surftemp <- expand.grid(no3_cat = levels(df_model$no3_cat),
                               surftemp = round(quantile(df_model$surftemp, 
                                                   probs = seq(0.10, 0.90, 0.2)), 0),
                               log_area = mean(df_model$log_area),
                               log_elev = mean(df_model$log_elev)) %>%
  add_epred_draws(n2o_mod6, resp = c("n2o", "n2oeq"), re_formula = ~ 1) %>%
  pivot_wider(names_from = .category, values_from = .epred) %>%
  mutate(n2o_pred = n2o,
         n2oeq_pred = n2oeq,
         sat_pred = n2o / n2oeq,
         surftemp = factor(surftemp))

@@

```{r plot_temp_area_effects, fig.align='center', fig.asp=1.166667, fig.width=8, }
plt_temp_area_effects
```

>>>>

```{r conditional_effects_mod_n2osat_temp_F, echo=FALSE, message=FALSE, warning=FALSE, cache.lazy=FALSE}
effect_no3_surftemp <- expand.grid(no3_cat = levels(df_model$no3_cat),
                               surftemp = round(quantile(df_model$surftemp, 
                                                   probs = seq(0.10, 0.90, 0.2)), 0),
                               log_area = mean(df_model$log_area),
                               log_elev = mean(df_model$log_elev)) %>%
  add_epred_draws(n2o_mod6, resp = c("n2o", "n2oeq"), re_formula = ~ 1) %>%
  pivot_wider(names_from = .category, values_from = .epred) %>%
  mutate(n2o_pred = n2o,
         n2oeq_pred = n2oeq,
         sat_pred = n2o / n2oeq,
         surftemp = factor(surftemp))

@@

legend1 <- ggpubr::get_legend(legend1)

@@

legend2 <- ggpubr::get_legend(legend2)

@@

```{r conditional_effects_mod_n2osat_area_F, echo=FALSE, message=FALSE, warning=FALSE, cache.lazy = FALSE}
effect_no3_area <- expand.grid(no3_cat = levels(df_model$no3_cat),
                               log_area = round(quantile(df_model$log_area, 
                                                   probs = seq(0.10, 0.90, 0.2)), 0),
                               surftemp = mean(df_model$surftemp),
                               log_elev = mean(df_model$log_elev)) %>%
  add_epred_draws(n2o_mod6, resp = c("n2o", "n2oeq"), re_formula = ~ 1) %>%
  pivot_wider(names_from = .category, values_from = .epred) %>%
  mutate(n2o_pred = n2o,
         n2oeq_pred = n2oeq,
         sat_pred = n2o / n2oeq,
         log_area = factor(log_area))

@@

```{r plot_area_effects, fig.align='center', fig.asp=1.166667, fig.width=8}
plt_area_effects
```

```{r conditional_effects_mod_n2osat_temp_area_F, echo=FALSE, message=FALSE, warning=FALSE, cache.lazy=FALSE}
effect_no3_surftemp <- expand.grid(no3_cat = levels(df_model$no3_cat),
                               surftemp = round(quantile(df_model$surftemp, 
                                                   probs = seq(0.10, 0.90, 0.2)), 0),
                               log_area = mean(df_model$log_area),
                               log_elev = mean(df_model$log_elev)) %>%
  add_epred_draws(n2o_mod6, resp = c("n2o", "n2oeq"), re_formula = ~ 1) %>%
  pivot_wider(names_from = .category, values_from = .epred) %>%
  mutate(n2o_pred = n2o,
         n2oeq_pred = n2oeq,
         sat_pred = n2o / n2oeq,
         surftemp = factor(surftemp))

@@

```{r plot_temp_area_effects, fig.align='center', fig.asp=1.166667, fig.width=8}
plt_temp_area_effects
```
